A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-07-11 paper/theor-experiment.tex
starting to fix verbatim sections

In order to compute the peaks, we employed an additional Python script.
This script was called in the \textsc{OPAL}~input file, after the simulation
  finished using the \texttt{SYSTEM} functionality.
Once the peaks (in a given range) were located, the two objectives
  (\ref{eq:swissfel:p1}) and (\ref{eq:swissfel:p2}) were computed and their
  values written into corresponding files.
The custom \texttt{fromFile} functor allows us to access the values stored in
  the peak finder Python script result files
%
%\vspace{0.2cm}
\begin{flushleft}
\noindent
\begin{Verbatim}[fontsize=\scriptsize]
rmsx:  OBJECTIVE, EXPR="statVariableAt("rms_x-err.dat", "var")";
emitx: OBJECTIVE, EXPR="statVariableAt("emit_x-err.dat", "var")";
match: OBJECTIVE, EXPR="fabs(statVariableAt("emit_x-peak.dat", "var") -
statVariableAt("rms_x-peak.dat", "var"))";
\end{Verbatim}
\end{flushleft}
\vspace{0.2cm}

\noindent
The design variables and the assembly of the multi-objective optimization problem
  can be included in the \textsc{OPAL}~input file as shown below:
%\vspace{0.2cm}
\begin{flushleft}
\noindent
\begin{Verbatim}[fontsize=\scriptsize]
d1: DVAR, VARIABLE="SIGX", LOWERBOUND="0.00025", UPPERBOUND="0.00029";
d2: DVAR, VARIABLE="FIND1_MSOL10_i", LOWERBOUND="110", UPPERBOUND="120";
d3: DVAR, VARIABLE="D_LAG_RGUN", LOWERBOUND="-0.1", UPPERBOUND="0.1";
d4: DVAR, VARIABLE="D_SOLPOS", LOWERBOUND="-0.05", UPPERBOUND="0.05";

@@

The maximum number of individuals per generation was fixed at 80, 
Each experiment was allowed to run for twenty four hours, with 
a maximum generation limit of 100. 
We reduced the seven objectives to the four needed to construct 
the Pareto fronts that would be the final goal of this study.
The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)\text{, } \text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
\lsnote{You could define $\varepsilon_{x1}$ to be $\varepsilon_{x} (s=s1)$ and similarly in the table and then use going forward to simplify notation}
The optimization parameters specific to OPAL input for ex-3 are given as an example.
Note the design variables defined in Section \ref{awaproblem}
precede the optimization parameters in the OPAL input file.

\vspace{0.2cm}
{\footnotesize \begin{verbatim}
	OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
	OUTPUT="optLinac_40nC",
	OUTDIR="results",
	OBJECTIVES = {rmss1, rmsx1, emitx1, de1, rmss2, rmsx2, emitx2},
	DVARS = {dv0, dv1, dv2, dv3, dv4, dv5, dv6, dv7},
	CONSTRAINTS = {c1, c2},
	INITIALPOPULATION=656,
	MAXGENERATIONS=200,
	NUM_MASTERS=1,
	NUM_COWORKERS=8,
	SIMTMPDIR="tmp",
	TEMPLATEDIR="tmpl",
	FIELDMAPDIR="fieldmaps",
	NUM_IND_GEN=328,
	GENE_MUTATION_PROBABILITY=0.8,
	MUTATION_PROBABILITY=0.8,
	RECOMBINATION_PROBABILITY=0.2;
	QUIT;
	\end{verbatim}}
\vspace{0.2cm}

@@

Equations (\ref{eq:awa:firstconstr}) to
(\ref{eq:awa:lastdvar}) define the charge, gun voltage, linac voltages, 
laser radius, gun phase, and linac cavity phases (in that order). 
These are parameters in the simulation 
that must be defined, but do not vary during the optimization.
%\vspace{-1em}
As introduced in Section \ref{ferrario}, we define the AWA optimization 
design variables, objectives, and constraints in the OPAL input file as shown in
the following code: %equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}).

\vspace{0.2cm}
{\footnotesize \begin{verbatim}

@@

	//Kicker apeture
	c1: CONSTRAINT, EXPR="fabs(statVariableAt('rms_x',16.5))<0.1";
	c2: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5))<0.1";
	c3: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5)-statVariableAt('rms_x',16.5))<0.005";

	OPTIMIZE, INPUT="tmpl/optLinac-40nC.tmpl",
	OUTPUT="optLinac-40nC",
	OUTDIR="results",
	OBJECTIVES = {rmss3, rmsx3, rmsy3, rmspx3, rmspy3, de3},
	DVARS = {dv0, dv1, dv4, dv5, dv6, dv7},
	CONSTRAINTS = {c1, c2, c3},
	INITIALPOPULATION=656,
	MAXGENERATIONS=200,
	NUM_MASTERS=1,
	NUM_COWORKERS=8,
	SIMTMPDIR="tmp",
	TEMPLATEDIR="tmpl",
	FIELDMAPDIR="fieldmaps",
	NUM_IND_GEN=328,
	GENE_MUTATION_PROBABILITY=0.01,
	MUTATION_PROBABILITY=0.01,
	RECOMBINATION_PROBABILITY=0.09;
	QUIT;

	\end{verbatim}}
\vspace{0.2cm}

>>>>

In order to compute the peaks, we employed an additional Python script.
This script was called in the \textsc{OPAL}~input file, after the simulation
  finished using the \texttt{SYSTEM} functionality.
Once the peaks (in a given range) were located, the two objectives
  (\ref{eq:swissfel:p1}) and (\ref{eq:swissfel:p2}) were computed and their
  values written into corresponding files.
The custom \texttt{fromFile} functor allows us to access the values stored in
  the peak finder Python script result files
%
%\vspace{0.2cm}
\begin{flushleft}
\begin{Verbatim}[fontsize=\scriptsize]
rmsx:  OBJECTIVE, EXPR="statVariableAt("rms_x-err.dat", "var")";
emitx: OBJECTIVE, EXPR="statVariableAt("emit_x-err.dat", "var")";
match: OBJECTIVE, EXPR="fabs(statVariableAt("emit_x-peak.dat", "var") -
statVariableAt("rms_x-peak.dat", "var"))";
\end{Verbatim}
\end{flushleft}
\vspace{0.2cm}

\noindent
The design variables and the assembly of the multi-objective optimization problem
  can be included in the \textsc{OPAL}~input file as shown below:
%\vspace{0.2cm}
\begin{flushleft}
\begin{Verbatim}[fontsize=\scriptsize]
d1: DVAR, VARIABLE="SIGX", LOWERBOUND="0.00025", UPPERBOUND="0.00029";
d2: DVAR, VARIABLE="FIND1_MSOL10_i", LOWERBOUND="110", UPPERBOUND="120";
d3: DVAR, VARIABLE="D_LAG_RGUN", LOWERBOUND="-0.1", UPPERBOUND="0.1";
d4: DVAR, VARIABLE="D_SOLPOS", LOWERBOUND="-0.05", UPPERBOUND="0.05";

@@

The maximum number of individuals per generation was fixed at 80, 
Each experiment was allowed to run for twenty four hours, with 
a maximum generation limit of 100. 
We reduced the seven objectives to the four needed to construct 
the Pareto fronts that would be the final goal of this study.
The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)\text{, } \text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
\lsnote{You could define $\varepsilon_{x1}$ to be $\varepsilon_{x} (s=s1)$ and similarly in the table and then use going forward to simplify notation}
The optimization parameters specific to OPAL input for ex-3 are given as an example.
Note the design variables defined in Section \ref{awaproblem}
precede the optimization parameters in the OPAL input file.
%
\vspace{0.2cm}
\begin{Verbatim}[fontsize=\scriptsize]
OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
OUTPUT="optLinac_40nC",
OUTDIR="results",
OBJECTIVES = {rmss1, rmsx1, emitx1, de1, rmss2, rmsx2, emitx2},
DVARS = {dv0, dv1, dv2, dv3, dv4, dv5, dv6, dv7},
CONSTRAINTS = {c1, c2},
INITIALPOPULATION=656,
MAXGENERATIONS=200,
NUM_MASTERS=1,
NUM_COWORKERS=8,
SIMTMPDIR="tmp",
TEMPLATEDIR="tmpl",
FIELDMAPDIR="fieldmaps",
NUM_IND_GEN=328,
GENE_MUTATION_PROBABILITY=0.8,
MUTATION_PROBABILITY=0.8,
RECOMBINATION_PROBABILITY=0.2;
QUIT;
\end{Verbatim}
\vspace{0.2cm}

@@

Equations (\ref{eq:awa:firstconstr}) to
(\ref{eq:awa:lastdvar}) define the charge, gun voltage, linac voltages, 
laser radius, gun phase, and linac cavity phases (in that order). 
These are parameters in the simulation 
that must be defined, but do not vary during the optimization.
%\vspace{-1em}
As introduced in Section \ref{ferrario}, we define the AWA optimization 
design variables, objectives, and constraints in the OPAL input file as shown in
the following code: %equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}). 
%\vspace{0.2cm}
\begin{Verbatim}[fontsize=\scriptsize]

@@

//Kicker apeture
c1: CONSTRAINT, EXPR="fabs(statVariableAt('rms_x',16.5))<0.1";
c2: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5))<0.1";
c3: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5)
			-statVariableAt('rms_x',16.5))<0.005";

OPTIMIZE, INPUT="tmpl/optLinac-40nC.tmpl",
OUTPUT="optLinac-40nC",
OUTDIR="results",
OBJECTIVES = {rmss3, rmsx3, rmsy3, rmspx3, rmspy3, de3},
DVARS = {dv0, dv1, dv4, dv5, dv6, dv7},
CONSTRAINTS = {c1, c2, c3},
INITIALPOPULATION=656,
MAXGENERATIONS=200,
NUM_MASTERS=1,
NUM_COWORKERS=8,
SIMTMPDIR="tmp",
TEMPLATEDIR="tmpl",
FIELDMAPDIR="fieldmaps",
NUM_IND_GEN=328,
GENE_MUTATION_PROBABILITY=0.01,
MUTATION_PROBABILITY=0.01,
RECOMBINATION_PROBABILITY=0.09;
QUIT;
\end{Verbatim}
\vspace{0.2cm}
